\documentclass{beamer}

\mode<presentation> {
\usetheme{Madrid}
}

\usepackage{graphicx} 
\usepackage{booktabs} 
\graphicspath{ {images/} }

\title[Feeder]{Feeder: The IITB Academic App}
 
\author{Enigma} 
\institute[IITB]
{
IIT Bombay \\
\medskip
\textbf{Group 01} 
}
\date{\today}

\begin{document}

\begin{frame}
\titlepage 
\end{frame}

\begin{frame}
\frametitle{Overview} 
\tableofcontents 
\end{frame}

\section{Contents}
\subsection{Motive}   

\begin{frame}
\frametitle{Motive}
Feeder was started by a group of IIT Bombay sophomores with a view to changing how courses function in their institute(and elsewhere). It is meant to bridge the communication gap between the students and the professors which in turn will improve the quality of the course being dished out. \\~\\

The instructors can receive constructive feedback on various aspects of the course and can thus dynamically change the ocurse structure for the better. The students too are sent reminders for the assignments and deadlines so that they do not miss out on important submissions and can plan their schedule more effectively.
\end{frame}



\section{Conclusion}
\subsection{Potential}
\subsection{Why Feeder}
\subsection{What Next} 
\subsection{Team Enigma} 

\begin{frame}
\frametitle{Potential}
\begin{itemize}
\item An app that can potentially improve the quality of courses dished out in universities
\item Helping bridge the communication gap between instructirs and students(Especually shy ones)
\item A much-required app for students who fall back on assignments and dealdines
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Why Feeder}
\begin{itemize}
\item There are students who start off on the project as soon as it is announced, and then there are some who tend to slack off and even forget about it. There are people who wish they had been reminded of an assignment, or even an exam that they have missed. Now imagine that we had “someone” who can organise all the academic schedules, be it an upcoming exam or a project deadline, and notify you as per your need. That "someone" is the feeder app that we humbly present to you
\item Every semester online feedback is collected for all theory as well as lab courses. But most of the times it’s just crying over spilt milk. Definitely the feedback helps future offerings of the course, but won’t it be much nicer if the feedback could be incorporated in the same offering. Feeder to the rescue!
\item Imagine if every college in the country used Feeder, there will be more accountability for the college and education in the country would improve
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What Next}
\begin{itemize}
\item Improving certain features in the application
\item Bolstering the security of the application
\item Including a provision for students to ask questions and interact with their peers
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{TEAM ENIGMA}
\centerline{IIT BOMBAY:ENIGMA}
\begin{itemize}
\item Tanuj Kaza(150050008)
\item Harsh Bansal(150050109)
\item Bhavya Bahl(150050110)
\end{itemize}
\end{frame}

\begin{frame}
\Huge{\centerline{THANK YOU}}
\end{frame}

\end{document}